Deciding Bitvector Termination with Program Synthesis

### 2014-06-27 papers/termination/table.tex
Sort benchmark names

@@

@@

svcomp26 & 23 & unk & true & true & false & false & 1 & 5 & term & 12.9s\\

svcomp1 & 17 & unk & true & true & false & false & 1 & 5 & term & 9.7s\\

svcomp9 & 12 & unk & true & unk & false & false & unk & 5 & term & 15.3s\\

svcomp37 & 22 & unk & true & true & false & false & 1 & 5 & term & 16.5s\\

svcomp3 & 15 & unk & true & true & false & false & unk & 5 & term & 39.8s\\

svcomp2 & 13 & unk & false & true & false & false & 1 & 5 & term & 7.1s\\

svcomp11 & 16 & unk & true & true & false & false & 1 & 5 & term & 41.3s\\

svcomp10 & 15 & unk & true & true & false & false & 1 & 5 & term & 30.9s\\

svcomp17 & 17 & unk & true & true & false & false & 1 & 5 & nonterm & 90.6s\\

>>>>

svcomp1 & 17 & unk & true & true & false & false & 1 & 5 & term & 9.6s\\

svcomp2 & 13 & unk & false & true & false & false & 1 & 5 & term & 10.2s\\

svcomp3 & 15 & unk & true & true & false & false & unk & 5 & unk & T/O\\

@@

svcomp9 & 12 & unk & true & unk & false & false & unk & 5 & term & 9.3s\\

svcomp10 & 15 & unk & true & true & false & false & 1 & 5 & term & 61.2s\\

svcomp11 & 16 & unk & true & true & false & false & 1 & 5 & unk & T/O\\

svcomp17 & 17 & unk & true & true & false & false & 1 & 5 & nonterm & 19.0s\\

svcomp26 & 23 & unk & true & true & false & false & 1 & 5 & term & 38.7s\\

svcomp37 & 22 & unk & true & true & false & false & 1 & 5 & term & 12.3s\\

@@
